Cluster Paper

### 2015-04-16 ms.tex
removed membership section
updated order, added some text

\begin{abstract}
\noindent
ABSTRACT GOES HERE!!
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Cras malesuada, ante eu scelerisque gravida, augue lacus ullamcorper metus, ac volutpat libero magna rutrum nisi. Interdum et malesuada fames ac ante ipsum primis in faucibus. Ut eget magna est. Nam quis maximus purus, feugiat facilisis lectus. Nulla mollis sodales felis a ullamcorper. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur rhoncus, ligula vel venenatis ornare, nisi massa sagittis orci, in hendrerit purus libero id mauris. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
\end{abstract}

@@

\section{ANALYSIS}

\subsection{Mock Observations}
\editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see. It should be more technical than the general discussion about what the survey hopes to accomplish, that'll go in the intro. A zoomed figure showing the tiling footprints would be appropriate.}

@@

\subsection{Dynamical Properties}
\subsubsection{Velocity Dispersion}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

@@

\subsection{Evidence of Substructure}
We leverage the large spectroscopic dataset to study the structural properties of the clusters. \cite{Pinkney1996} determine, from a comparison of five different methods that the Dressler-Shectman (DS) test \citep{Dressler1988} is the most sensitive to the presence of substructure.

@@

%\subsection{Membership}
%It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster. To reject these interlopers we employ two methods. For clusters with 20 or more $Q=0$ redshifts we use the  ``shifting gapped" method of \cite{Fadda1996}. This procedure combines both the positional and velocity information. Galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 galaxies. The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
%\begin{equation}
%	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
%\end{equation}
%where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster. Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper. The procedure repeats until the number of galaxies stabilizes in the bin.

%For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
%\begin{equation}
%	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
%\end{equation}
%and
%\begin{equation}
%	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
%\end{equation}
%where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.

%The observed velocity dispersion, $\sigma_v$, of each cluster is calculated in two different ways. For clusters with at least 15 confirmed members, we use the biweight scale estimator \citep{Beers1990} which is less susceptible to outliers which may remain after the rejection of non-cluster members.

%For galaxy clusters with fewer than 15 members, we employ the gapper estimator \citep{Beers1990} which provides accurate dispersions for groups as small as 5 members \citep{Hou2009}. The gapped estimator is given by
%\begin{equation}
%	\sigma_v = 1.135c \frac{\sqrt{\pi}}{n(n-1)} \sum_{i=1}^{n-1} w_i g_i
%\end{equation}
%where the weights are $w_i = i(n-i)$ and the gaps $g_i = z_{i+1} -z_i$. The factor of 1.135 is from \cite{Wilman2005} which corrects for the $2\sigma$ redshift space cut applied during membership determination.

@@

\section{IMPROVEMENT}
\section{SUMMARY}

\bibliography{master}

>>>>

\begin{abstract}
\noindent
ABSTRACT GOES HERE!!
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

@@

\section{Mock Observations}
\editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see. It should be more technical than the general discussion about what the survey hopes to accomplish, that'll go in the intro. A zoomed figure showing the tiling footprints would be appropriate.}

@@

\section{Recovery of Cluster Parameters, Full Knowledge}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\subsection{Cluster Redshift}
The accurate determination of the cluster redshift is crucial to the reliability of all following measurements. An incorrect cluster redshift introduces errors into the measured line of sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster.

\subsection{Line of Sight Velocity Dispersion}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

@@

\section{Evidence of Substructure}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\subsection{From VD profiles}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\subsection{Mod-Dominance}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\subsection{Dressler-Schectman Test}
We leverage the large spectroscopic dataset to study the structural properties of the clusters. \cite{Pinkney1996} determine, from a comparison of five different methods that the Dressler-Shectman (DS) test \citep{Dressler1988} is the most sensitive to the presence of substructure.

@@

@@

\section{IMPROVEMENT}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\section{SUMMARY}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\bibliography{master}
